Capturing the shape of our experiences and how we remember them

### 2018-08-21 paper/main.tex
added a few more references

While our experiences often change gradually, they can also change rapidly (e.g. walking through a doorway) \citep{RadvZack17}. Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17}. Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18}.  In other words, the interplay between stable and transient temporal dynamics may impose structure on memories for those experiences. There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.  However, whether people verbally recount their experiences in a way that is structured around events has not been established.

>>>>

While our experiences often change gradually, they can also change rapidly (e.g. walking through a doorway) \citep{RadvZack17}. Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}. Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, EzzyDava11, DuBrDava13}.  In other words, the interplay between stable and transient temporal dynamics may impose structure on memories for those experiences. There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.  However, whether people verbally recount their experiences in a way that is structured around events has not been established.
